Density-dependent selection in evolutionary genetics: a lottery model of Grime's triangle

### 2017-04-03 manuscript.tex
latest

\section*{•}

@@

in expanding (e.g. humans) or seasonally-cycling (e.g. \textit{Drosophila}) populations \citep{bergland_14}.

@@

>>>>

\section*{Stable polymorphisms due to cyclical population density}

We now consider the behaviour of Eq. \eqref{eq:master} when population density cycles periodically. For example, natural \textit{Drosophila}) populations undergo large seasonal density cycles, expanding rapidly in the warmer months when fruit is abundant, and being carried through the colder months by a much smaller number of dormant individuals. Allele frequencies at many loci [check] also cycle seasonally \citep{bergland_14}.

This illustrates the density-dependent behaviour of Eq. \eqref{eq:master}.

@@

in expanding (e.g. humans) or seasonally-cycling (e.g. .

@@

\begin{figure}
\centering
\includegraphics[scale=1]{fluctuatingselection.pdf}
\caption{\label{fig:axes} The realization of Grime's triangle in our model. Schematic representation of the triangular space bounded by the low/high extremes of stress/disturbance. The low-$T$ interpretation of stress is also shown. The vertices of the triangles correspond to different environmental extremes. Selection favors different traits at each vertex, leading to different trait clusters.} 
\end{figure}
